---
title: "ShinySAMPDavid"
author: "Hyeonjoon David Park"
date: "`r Sys.Date()`"
output: 
    html_document: rmarkdown::html_vignette
    df_print: paged
    highlights: pygments
    theme: spacelab
    toc: yes
    toc_float: yes
vignette: >
  %\VignetteIndexEntry{ShinySAMPDavid}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
runtime: shiny
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ShinySAMPDavid)
```

This vignette briefly introduces basic construction and usage of the package "ShinySAMPDavid" I made.

# Using the Shiny server

Using the shiny dashboard template create widgets to input `n`, `iter`, `mu`, $\sigma_{ij}$ the output will be the plots: 2d density plot of $\bar{X}$ and histogram of $\theta$. I will leave it to you to make the suitable bounds on the widget variables (remember that the covariance matrix is symmetrical)

```{r}
ui = uifunction(300,7000,0,0,200,500,50)

shinyApp(ui, server)
```
